First Season MWA EoR Power Spectrum Results at Redshift 7

### 2016-04-26 ms.tex
Added TODOs for pipeline comparison
added mahsa as author

\affilauthorlist{
A.~P.~Beardsley\affils{ASU,UW}\myemail,
B.~J.~Hazelton\affils{UW,UWeSci},
I.~S.~Sullivan\affils{UW},
J.~C.~Pober\affils{Brown,UW},
P.~Carroll\affils{UW},
N.~Barry\affils{UW},
M.~F.~Morales\affils{UW}, 
Daniel~C.~Jacobs\affils{ASU},
G.~Bernardi\affils{SKASA,RU,CfA},
Judd~D.~Bowman\affils{ASU},
M.~P.~Busch\affils{ASU},
F.~Briggs\affils{ANU,CAASTRO},
R.~J.~Cappallo\affils{Haystack}, 
B.~E.~Corey\affils{Haystack}, 
A.~de~Oliveira-Costa\affils{MIT},
Joshua~S.~Dillon\affils{Berkeley, RAL, BCCP,MIT},
D.~Emrich\affils{Curtin},
A.~Ewall-Wice\affils{MIT},
L.~Feng\affils{MIT},
B.~M.~Gaensler\affils{USydney,CAASTRO,Dunlap}, 
R.~Goeke\affils{MIT},
L.~J.~Greenhill\affils{CfA},
J.~N.~Hewitt\affils{MIT},
N.~Hurley-Walker\affils{Curtin},
M.~Johnston-Hollitt\affils{Victoria},
D.~L.~Kaplan\affils{UWisc}, 
J.~C.~Kasper\affils{UMichigan,CfA}, 
HS Kim\affils{UMelbourne,CAASTRO},
E.~Kratzenberg\affils{Haystack}, 
E.~Lenc\affils{USydney,CAASTRO},
J.~Line\affils{UMelbourne,CAASTRO},
A.~Loeb\affils{CfA},
C.~J.~Lonsdale\affils{Haystack}, 
M.~J.~Lynch\affils{Curtin}, 
B.~McKinley\affils{UMelbourne,CAASTRO},
S.~R.~McWhirter\affils{Haystack},
D.~A.~Mitchell\affils{CASS,CAASTRO}, 
E.~Morgan\affils{MIT}, 
A.~R.~Neben\affils{MIT},
N.~Thyagarajan\affils{ASU},
D.~Oberoi\affils{Tata}, 
A.~R.~Offringa\affils{ASTRON,CAASTRO}, 
S.~M.~Ord\affils{Curtin,CAASTRO},
S. Paul\affils{RRI},
B.~Pindor\affils{UMelbourne,CAASTRO},
T.~Prabu\affils{RRI}, 
P.~Procopio\affils{UMelbourne,CAASTRO},
J.~Riding\affils{UMelbourne,CAASTRO},
A.~E.~E.~Rogers\affils{Haystack}, 
A.~Roshi\affils{NRAO}, 
N.~Udaya~Shankar\affils{RRI}, 
Shiv~K.~Sethi\affils{RRI},
K.~S.~Srivani\affils{RRI}, 
R.~Subrahmanyan\affils{RRI,CAASTRO}, 
M.~Tegmark\affils{MIT},
S.~J.~Tingay\affils{Curtin,CAASTRO}, 
C.~M.~Trott\affils{Curtin,CAASTRO},
M.~Waterson\affils{Curtin,ANU},
R.~B.~Wayth\affils{Curtin,CAASTRO}, 
R.~L.~Webster\affils{UMelbourne,CAASTRO}, 
A.~R.~Whitney\affils{Haystack}, 
A.~Williams\affils{Curtin}, 
C.~L.~Williams\affils{MIT},
C.~Wu\affils{UWA},
J.~S.~B.~Wyithe\affils{UMelbourne,CAASTRO}
}

@@

\subsection{Comparison with reference pipeline}\label{subsec:ref_pipe}
\textcolor{red}{Will inject comparison with RTS/CHIPS here.}

>>>>

\affilauthorlist{
A.~P.~Beardsley\affils{ASU,UW}\myemail,
B.~J.~Hazelton\affils{UW,UWeSci},
I.~S.~Sullivan\affils{UW},
J.~C.~Pober\affils{Brown,UW},
P.~Carroll\affils{UW},
N.~Barry\affils{UW},
M.~F.~Morales\affils{UW}, 
Daniel~C.~Jacobs\affils{ASU},
G.~Bernardi\affils{SKASA,RU,CfA},
Judd~D.~Bowman\affils{ASU},
M.~P.~Busch\affils{ASU},
F.~Briggs\affils{ANU,CAASTRO},
R.~J.~Cappallo\affils{Haystack}, 
B.~E.~Corey\affils{Haystack}, 
A.~de~Oliveira-Costa\affils{MIT},
Joshua~S.~Dillon\affils{Berkeley, RAL, BCCP,MIT},
D.~Emrich\affils{Curtin},
A.~Ewall-Wice\affils{MIT},
L.~Feng\affils{MIT},
B.~M.~Gaensler\affils{USydney,CAASTRO,Dunlap}, 
R.~Goeke\affils{MIT},
L.~J.~Greenhill\affils{CfA},
J.~N.~Hewitt\affils{MIT},
N.~Hurley-Walker\affils{Curtin},
M.~Johnston-Hollitt\affils{Victoria},
D.~L.~Kaplan\affils{UWisc}, 
J.~C.~Kasper\affils{UMichigan,CfA}, 
HS Kim\affils{UMelbourne,CAASTRO},
E.~Kratzenberg\affils{Haystack}, 
E.~Lenc\affils{USydney,CAASTRO},
J.~Line\affils{UMelbourne,CAASTRO},
A.~Loeb\affils{CfA},
C.~J.~Lonsdale\affils{Haystack}, 
M.~J.~Lynch\affils{Curtin}, 
B.~McKinley\affils{UMelbourne,CAASTRO},
S.~R.~McWhirter\affils{Haystack},
D.~A.~Mitchell\affils{CASS,CAASTRO}, 
E.~Morgan\affils{MIT}, 
A.~R.~Neben\affils{MIT},
N.~Thyagarajan\affils{ASU},
D.~Oberoi\affils{Tata}, 
A.~R.~Offringa\affils{ASTRON,CAASTRO}, 
S.~M.~Ord\affils{Curtin,CAASTRO},
S. Paul\affils{RRI},
B.~Pindor\affils{UMelbourne,CAASTRO},
T.~Prabu\affils{RRI}, 
P.~Procopio\affils{UMelbourne,CAASTRO},
M.~Rahimi\affils{UMelbourne},
J.~Riding\affils{UMelbourne,CAASTRO},
A.~E.~E.~Rogers\affils{Haystack}, 
A.~Roshi\affils{NRAO}, 
N.~Udaya~Shankar\affils{RRI}, 
Shiv~K.~Sethi\affils{RRI},
K.~S.~Srivani\affils{RRI}, 
R.~Subrahmanyan\affils{RRI,CAASTRO}, 
M.~Tegmark\affils{MIT},
S.~J.~Tingay\affils{Curtin,CAASTRO}, 
C.~M.~Trott\affils{Curtin,CAASTRO},
M.~Waterson\affils{Curtin,ANU},
R.~B.~Wayth\affils{Curtin,CAASTRO}, 
R.~L.~Webster\affils{UMelbourne,CAASTRO}, 
A.~R.~Whitney\affils{Haystack}, 
A.~Williams\affils{Curtin}, 
C.~L.~Williams\affils{MIT},
C.~Wu\affils{UWA},
J.~S.~B.~Wyithe\affils{UMelbourne,CAASTRO}
}

@@

\subsection{Comparison with reference pipeline}\label{subsec:ref_pipe}
\textcolor{red}{Will inject comparison with RTS/CHIPS here.}
% ADAM: Motivation why a pipeline is being discussed
% MAHSA: Summary of RTS to power spectrum (e.g. calibration, etc)
% MAHSA QA: - bad day, forward reference Jordan et al, Beam nulls - fixed for future analysis
% CATH: Plots
%     by pointing - diff zenith vs +2 
%	2D PS vs redshift
%	1D
